R Notebook

### 2024-05-30 02_paper/02_study/02_fitbit paper/analysis_270423.Rmd
fb

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = TRUE,
	error = FALSE,
	message = FALSE,
	warning = FALSE
)
```

```{r}
library(needs)
needs(ltm,
      xtable,
      broom,
      ppcor,
      jtools,
      lm.beta,
      janitor,
      lubridate,
      readxl,
      ggthemes,
      gridExtra,
      imputeTS,
      DescTools,
      cowplot,
      rstatix,
      ggpubr,
      lme4,
      lmerTest,
      viridis,
      gridExtra,
      gridtext,
      magrittr,
      PerformanceAnalytics,
      Hmisc,
      corrplot,
      tidyverse,
      ggplot2,
      lavaan,
      lm.beta)

@@

# Plots

```{r fig.width = 10,results='hide',fig.keep='all'}

@@

@@

# Slopes and Intercepts

```{r}
df_regression <- 
  main %>% 
  filter(time_span != "overall") %>%
  dplyr::select("ID", "time_span","time","heart_rate_std","heart_rate") %>% 
  distinct() %>% 
  mutate(time = time / 60) %>% 
  mutate(ID = as_factor(ID),
         Phase = factor(time_span,
                           levels = c("preparation","teaching","post","interview","end"),
                            labels = c("Pre Teaching Phase","Teaching Phase","Post Teaching Phase","Interview Phase","End Phase")
                           )
         )

@@

# t-Tests 
## using heart rate means

```{r}
df_ttest <- 
  df_regression %>% 
  group_by(ID, time_span) %>% 
  summarise(mean_heart_rate = mean(heart_rate_std)) %>% 
  ungroup()
```

## Teaching vs. Pre-Teaching (mean HR)

@@

## Teaching vs. End (mean HR)

```{r}
df_ttest %$% 
  t.test(x = .$mean_heart_rate[.$time_span == "teaching"],
         y = .$mean_heart_rate[.$time_span == "end"],
         paired = T)

@@

# t-Tests 
## using mean Slope

```{r}
df_ttest_slope <- 
  fix_models %>% 
  group_by(id, Phase) %>% 
  summarise(mean_slope = mean(slope)) %>% 
  ungroup()
```

## Teaching vs. Interview (mean slope)

```{r}
df_ttest_slope %$% 
  t.test(x = .$mean_slope[.$Phase == "Teaching Phase"],
         y = .$mean_slope[.$Phase == "Interview Phase"],
         paired = T)

df_ttest_slope %$% 
  CohenD(x = .$mean_slope[.$Phase == "Teaching Phase"],
         y = .$mean_slope[.$Phase == "Interview Phase"],
         pooled = T)
```

## Teaching vs. End (mean slope)

@@

## Interview vs. End (mean slope)

```{r}
df_ttest_slope %$% 
  t.test(x = .$mean_slope[.$Phase == "Interview Phase"],
         y = .$mean_slope[.$Phase == "End Phase"],
         paired = T)

@@

### Correlation

## age x teaching experience
``` {r}
main %>% 
  filter(time_span == "overall") %>% 
  group_by(ID) %>% 
  select(ID,
         teaching_experience,
         age) -> teach_gender

@@

# Multiple Linear Regression (Mean)
```{r}
main %>% 
  group_by(ID, time_span) %>% 
  summarise(disruption_factor = mean(disruption_factor,
                                     na.rm = T),
            confidence_factor = mean(confidence_factor,
                                     na.rm = T),
            teaching_experience = mean(teaching_experience),
            heart_rate = mean(heart_rate_std)
            ) %>% 
  ungroup() -> data_regression_mean

@@

# Multiple Linear Regression (Slope)
```{r}

@@

# Multiple Linear Regression (Slope)

# Pre Teaching Phase
```{r echo = FALSE, results='asis'}
df_multi <- 
  main %>% 
  select("ID", "disruption_factor", "confidence_factor", "teaching_experience") %>% 
  distinct() %>% 
  group_by(ID) %>% 
  summarise(disruption_factor = mean(disruption_factor, na.rm = T),
            confidence_factor = mean(confidence_factor, na.rm = T),
            teaching_experience) %>% 
  ungroup() %>% 
  mutate(id = as.character(ID)) %>% 
  distinct() %>% 
  right_join(x = .,
            y = fix_models,
            by = "id")
  # mutate(posneg = if_else(condition = slope < 0,
  #                         true = "negative",
  #                         false = "positive"))

@@

# Teaching Phase

@@

# Interview Phase

@@

# End Phase

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = TRUE,
	error = FALSE,
	message = FALSE,
	warning = FALSE
)
```
# Packages & read in data
```{r}
library(needs)
needs(ltm,
      xtable,
      broom,
      ppcor,
      jtools,
      lm.beta,
      janitor,
      lubridate,
      readxl,
      ggthemes,
      gridExtra,
      imputeTS,
      DescTools,
      cowplot,
      rstatix,
      ggpubr,
      lme4,
      lmerTest,
      viridis,
      gridExtra,
      gridtext,
      magrittr,
      PerformanceAnalytics,
      Hmisc,
      corrplot,
      tidyverse,
      ggplot2,
      lavaan,
      lm.beta,
      psych,
      stats)

@@

# Plots
```{r fig.width = 10,results='hide',fig.keep='all'}

@@

## Box Plot (over 81 participants) 
box_plot <-
  main %>% 
  filter(time_span != "overall") %>%   
  dplyr::select("ID",
         "time_span",
         "heart_rate_std") %>% 
  mutate(time_span = fct_recode(time_span,
                                "Pre-teaching Interval" = "pre",
                                "Teaching Interval" = "main",
                                "Post-teaching Interval" = "subsequent",
                                "Interview Interval" = "interview",
                                "End Interval" = "after"
                                ),
         time_span = factor(time_span,
                            levels = c("Pre-teaching Interval",
                                       "Teaching Interval",
                                       "Post-teaching Interval",
                                       "Interview Interval",
                                       "End Interval"
                                       ),
                            labels = c("Pre-Teaching\nInterval",
                                       "Teaching\nInterval",
                                       "Post-Teaching\nInterval",
                                       "Interview\nInterval",
                                       "End\nInterval")
                            )
         ) %>%
  distinct() %>% 
  group_by(ID, time_span) %>%
  summarise(mean_hr_std = 
              mean(heart_rate_std, 
                   na.rm = TRUE)
            ) %>% 
  ggplot(mapping = aes(x = time_span,
                       y = mean_hr_std
                       )
         ) +
  geom_boxplot()+
  scale_y_continuous(breaks=seq(-2, 2, 1), 
                     limits=c(-2, 2)
                     ) +   
  # geom_jitter(width = 0.2) +
  theme_apa() + 
  theme(axis.text.x = 
          element_text(
            color="black",
            size = 12),
        plot.caption = element_text(hjust = 0)
        ) + 
  labs(x = "",
       y = "Standardized Mean Heart Rate",
       caption = expression(
         paste(italic("Note: N"), 
               "= 81 participants per interval. Fig. shows median (bold line), interquartile range (box) and outliers (dots)."
         )
       ))

box_plot

ggsave(filename = "plots_publication/box_plot.png",
       plot = box_plot,
       width = 20,
       height = 12,
       units = "cm")

@@

# Slopes and Intercepts
```{r}
df_regression <- 
  main %>% 
  filter(time_span != "overall") %>%
  dplyr::select("ID", "time_span","time","heart_rate_std","heart_rate") %>% 
  distinct() %>% 
  mutate(time = time / 60) %>% 
  mutate(ID = as_factor(ID),
         Phase = factor(time_span,
                           levels = c("preparation","teaching","post","interview","end"),
                            labels = c("Pre Teaching Phase","Teaching Phase","Post Teaching Phase","Interview Phase","End Phase")
                           )
         )

@@

# t-Tests 
## using heart rate means
```{r}
df_ttest <- 
  df_regression %>% 
  group_by(ID, time_span) %>% 
  summarise(mean_heart_rate = mean(heart_rate_std)) %>% 
  ungroup()
```
## Teaching vs. Pre-Teaching (mean HR)

@@

## Teaching vs. End (mean HR)
```{r}
df_ttest %$% 
  t.test(x = .$mean_heart_rate[.$time_span == "teaching"],
         y = .$mean_heart_rate[.$time_span == "end"],
         paired = T)

@@

## ANOVA & planned constrasts
```{r}
# Data wrangling - preparing data for ANOVA
df_anova <-
  main %>% 
  filter(time_span != "overall") %>%   
  dplyr::select("ID",
         "time_span",
         "heart_rate_std") %>% 
  mutate(time_span = fct_recode(time_span,
                                "Pre-teaching interval" = "pre",
                                "Teaching interval" = "main",
                                "Post-teaching interval" = "subsequent",
                                "Interview interval" = "interview",
                                "End interval" = "after"
                                ),
         time_span = factor(time_span,
                            levels = c("Pre-teaching interval",
                                       "Teaching interval",
                                       "Post-teaching interval",
                                       "Interview interval",
                                       "End interval"
                                       )
                            )
         ) %>%
  distinct() %>% 
  group_by(ID, time_span) %>%
  summarise(mean_hr_std = mean(heart_rate_std, na.rm = TRUE))

# Counting participants in individual phases
table(df_anova['time_span'])

# descriptive analysis
describeBy(df_anova$mean_hr_std,
           df_anova$time_span)

# Visualization
bxp <- ggboxplot(df_anova, x = "time_span", y = "mean_hr_std", add = "point")
bxp

# Check for outliers
outliers <-
  df_anova %>%
  group_by(time_span) %>%
  identify_outliers(mean_hr_std)

# check for normality assumption --> can be checked by computing Shapiro-Wilk test for each time point. If the data is normally distributed, the p-value should be greater than 0.05
norm_assump <-
  df_anova %>%
  group_by(time_span) %>%
  shapiro_test(mean_hr_std)

# QQ plot draws the correlation between a given data and the normal distribution. 
plot <- 
  ggqqplot(df_anova, "mean_hr_std", facet.by = "time_span")

df_anova_subset <- subset(df_anova, select = c(time_span, mean_hr_std))

# # anova
# res.aov <- rstatix::anova_test(data = df_anova_subset,
#                                dv = mean_hr,
#                                wid = ,
#                                within = time_span)
# get_anova_table(res.aov)

# anova
df_anova_phase <- 
  aov(df_anova_subset$mean_hr_std ~ df_anova_subset$time_span)
summary(df_anova_phase)

# effect size for ANOVA
DescTools::EtaSq(df_anova_phase)
f = sqrt (0.7202944/ (1-0.7202944))

# planned constrasts
model <- aov(mean_hr_std ~ time_span, data = df_anova_subset)
summary (model)

contrast1 <- c(-1, 1, 0, 0, 0)
contrast2 <- c(0, 1, -1, 0, 0)
contrast3 <- c(0, 1, 0, -1, 0)
contrast4 <- c(0, 1, 0, 0, -1)

contrasts(df_anova_subset$time_span) <- cbind(contrast1,
                                              contrast2,
                                              contrast3,
                                              contrast4)

model2 <- aov(mean_hr_std ~ time_span, data = df_anova_subset)
summary(model2)

summary.aov(model2, 
            split = list (time_span = list ("Teaching interval vs. Pre-teaching interval" = 1,
                                            "Teaching interval vs. Post-teaching interval" = 2,
                                            "Teaching interval vs. Interview interval" = 3,
                                            "Teaching interval vs. End interval" = 4
                                            )
                          )
            )

# t-Tests 
## using mean Slope 
```{r}
df_ttest_slope <- 
  fix_models %>% 
  group_by(id, Phase) %>% 
  summarise(mean_slope = mean(slope)) %>% 
  ungroup()
```

## Teaching vs. Interview (mean slope)
```{r}
df_ttest_slope %$% 
  t.test(x = .$mean_slope[.$Phase == "Teaching Phase"],
         y = .$mean_slope[.$Phase == "Interview Phase"],
         paired = T)

df_ttest_slope %$% 
  CohenD(x = .$mean_slope[.$Phase == "Teaching Phase"],
         y = .$mean_slope[.$Phase == "Interview Phase"],
         pooled = T)
```
## Teaching vs. End (mean slope)

@@

## Interview vs. End (mean slope)
```{r}
df_ttest_slope %$% 
  t.test(x = .$mean_slope[.$Phase == "Interview Phase"],
         y = .$mean_slope[.$Phase == "End Phase"],
         paired = T)

@@

### Correlation 
## age x teaching experience
``` {r}
main %>% 
  filter(time_span == "overall") %>% 
  group_by(ID) %>% 
  select(ID,
         teaching_experience,
         age) -> teach_gender

@@

# Multiple Linear Regression (Mean) -- LOOP
```{r}
main %>% 
  group_by(ID, time_span) %>% 
  summarise(disruption_factor = mean(disruption_factor,
                                     na.rm = T),
            confidence_factor = mean(confidence_factor,
                                     na.rm = T),
            teaching_experience = mean(teaching_experience),
            heart_rate = mean(heart_rate_std)
            ) %>% 
  ungroup() -> data_regression_mean

@@

```
# Multiple Linear Regression (Slope) -- LOOP
```{r}

@@

# Multiple Linear Regression (Slope)
# Pre Teaching Phase
```{r echo = FALSE, results='asis'}
df_multi <- 
  main %>% 
  select("ID", "disruption_factor", "confidence_factor", "teaching_experience") %>% 
  distinct() %>% 
  group_by(ID) %>% 
  summarise(disruption_factor = mean(disruption_factor, na.rm = T),
            confidence_factor = mean(confidence_factor, na.rm = T),
            teaching_experience) %>% 
  ungroup() %>% 
  mutate(id = as.character(ID)) %>% 
  distinct() %>% 
  right_join(x = .,
            y = fix_models,
            by = "id")
  # mutate(posneg = if_else(condition = slope < 0,
  #                         true = "negative",
  #                         false = "positive"))

@@

```
# Teaching Phase

@@

# Interview Phase
```{r echo = FALSE, results='asis'}
df_multi <- 
  main %>% 
  select("ID", "disruption_factor", "confidence_factor", "teaching_experience") %>% 
  distinct() %>% 
  group_by(ID) %>% 
  summarise(disruption = mean(disruption_factor, na.rm = T),
            confidence = mean(confidence_factor, na.rm = T),
            teaching_experience) %>% 
  ungroup() %>% 
  mutate(id = as.character(ID)) %>% 
  distinct() %>% 
  right_join(x = .,
            y = fix_models,
            by = "id") %>% 
  mutate(posneg = if_else(condition = slope < 0,
                          true = "negative",
                          false = "positive"))

@@

# End Phase
```{r echo = FALSE, results='asis'}
df_multi <- 
  main %>% 
  select("ID", "disruption_factor", "confidence_factor", "teaching_experience") %>% 
  distinct() %>% 
  group_by(ID) %>% 
  summarise(disruption = mean(disruption_factor, na.rm = T),
            confidence = mean(confidence_factor, na.rm = T),
            teaching_experience) %>% 
  ungroup() %>% 
  mutate(id = as.character(ID)) %>% 
  distinct() %>% 
  right_join(x = .,
            y = fix_models,
            by = "id") %>% 
  mutate(posneg = if_else(condition = slope < 0,
                          true = "negative",
                          false = "positive"))
